Topological Equivariant Artist Model

### 2022-02-23 slides/main.tex
compiles up to construction

\begin{frame}{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}
    \onslide<|handout:1>{
    \adjustbox{scale=3, center}{
        \begin{tikzcd}[ampersand replacement=\&]
            \& {} \arrow[dd, "\alpha" , Rightarrow, shorten=1.5em, color=nattran] \&             \\
          \textcolor{source}{\mathcal{C}} \arrow[rr, "F", bend left, color=functor, maps to] \arrow[rr, "G"', bend right, color=functor, maps to] \& \& \textcolor{target}{\mathcal{D}} \\
            \& {} \&            
          \end{tikzcd}}}
\end{frame}

@@

@@

    \only<0|handout:1>{

@@

    \only<0|handout:4>{

@@

    \only<0|handout:2>{

@@

    \only<0|handout:5>{

@@

            \item $\cgamma{\opensetc}{\gtotalc\restriction_{\opensetc}} \ni \gsectionc: \opensetc \rightarrow \gfiberc\restriction_{\opensetc}$
            \item $\vindexpushc\gsectionc(\dbasepointc) = \gsectionc\restriction_{\vindexpre(\dbasepointc)} = \gsectionc(\gbasepointc) \forall \gbasepointc \in \vindexpre(\dbasepointc)$ 

@@

@@

\begin{frame}
    \frametitle<0|handout:1>{Artist: $\vartistc: \sheafc_{\dbasec, \dtotalc} \rightarrow \sheafc_{\gbasec, \gtotalc}$}
    \frametitle<0|handout:2>{Data Space: $\vartistc_{\opensetc}: \sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\Rightarrow} \vindexpushc\sheafc_{\gbasec, \gtotalc}$}
    \frametitle<0|handout:3>{Display Space: $\vartist_{\opensetgc}: \vindexpullc\sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\Rightarrow} \sheafc_{\gbasec, \gtotalc}$}
    \frametitle<0|handout:4>{Artist: $\vartistc: \cgamma{\opensetc}{\dtotalc} \rightarrow \cgamma{\opensetgc}{\gtotalc}$}

    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<0|handout:1>{\sheafc_{\gbasec, \gtotalc}} 
          \onslide*<0|handout:4>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}}
          \onslide*<0|handout:1,4>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \& \& 
          \onslide*<0|handout:1>{\vindexpushc\sheafc_{\gbasec, \gtotalc}}
          \onslide*<0|handout:4>{\cgamma{\opensetc}{\vindexpushc \gtotalc\restriction_{\opensetc}}}
          \\
          \& \& \\
          \onslide*<0|handout:1>{\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}}
          \onslide*<0|handout:4>{\cgamma{\opensetgc}{\vindexpullc \dtotalc\restriction_{\opensetgc}}}
          \onslide*<0|handout:1,4>{\arrow[uu, "\vartistc_{\opensetgc}", color=artist, Rightarrow]}
          \&  \& 
          \onslide*<0|handout:1>{\sheafc_{\dbasec, \dtotalc}}
          \onslide*<0|handout:4>{\cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}}
          \onslide*<0|handout:1,4>{\arrow[ll, "\textcolor{functor}{\vindexpull}", color=functor]} 
          \onslide*<0|handout:1,4>{\arrow[uu, "\vartistc_{\opensetc}"', color=artist, Rightarrow]}
          \onslide*<4-|handout:1,4>{\arrow[lluu, "\vartistc"' description, dashed, color=artist, Rightarrow]}
        \end{tikzcd}
    \end{equation*}

@@

\subsection{Equivariance}

\begin{frame}{Transform Data}
    \begin{block}{Fiber Bundle Category}
        \begin{description}[style=newline]
            \item[object] $\dfiberc \hookrightarrow \dtotalc \xrightarrow{\pi} \dbasec$
            \item[morphisms] $\dfuncc: \dtotalc \rightarrow \dtotalc$ 
        \end{description}
    \end{block}
    \begin{block}{Fiber Category}
        The fiber $\dfiberc$ is the sole object of an arbitrary category $\mathcal{C}$.
        The morphisms on the fiber are $Hom(\dfiberc, \dfiberc)$
    \end{block}

@@

    \begin{alertblock}{}
        \begin{align*}
            \vartistc(\dsectionc^{a}) = \vartistc(\dsectionc^{b}) &\centernot\implies \dsectionc^a = \dsectionc^b \\
            \vartistc(\dsectionc^{a})  = \vartistc(\dsectionc^{b}) &\implies \vartistc(\dfuncc_{\dtotalc}(\dsectionc^{a})) = \vartistc(\dfuncc_{\dtotalc}(\dsectionc^{b}))
        \end{align*}
    \end{alertblock}
\end{frame}

\begin{comment}
\begin{frame}{Equivariant $\dfunchc$}
    \note{Maybe move to implementation section}
        \begin{equation*}
            \begin{tikzcd}[ampersand replacement=\&]
            \opensetgc 
            \arrow[rr, "\vindexc", color=functor] 
            \arrow[dd, "\dfunchc_{\gbasec}"', dashed, color=action] 
            \&  \& 
            \opensetc 
            \arrow[dd, "\dfunchc_{\dbasec}", color=action] \\
            \&  \& \\
            \opensetgc^{\prime} 
            \arrow[rr, "\vindexc"', color=functor]
            \&  \& 
            \opensetc^{\prime}\\
            \underbrace{\dbasec \times {[0,1]}^{m}}_{\gbasec} \arrow[rr,"\vindex", maps to, color=functor] \& \& \dbasec
            \end{tikzcd}
        \end{equation*}
\end{frame}

@@

\begin{frame}{Complex data}
    \begin{description}[style=newline]
        \item[combining continuities]{given $\dbasepointc_{a} \in \dbasec_{c} \subset \dbasec_{a}$ and $\dbasepointc_{b} \in \dbasec_{c} \subset \dbasec_{b}$, if $\dbasepointc_{a} = \dbasepointc_{b}$ then $\equivc(\dsectionc(\dbasepointc_{a})) = \equivc(\dsectionc(\dbasepointc_{b}))$ for all $\dbasepointc_{a}, \dbasepointc_{b} \in \dbasec_{a}\bigsqcup\limits_{\dbasec_{c}} \dbasec_{b}$}
        \item[shared fibers]{
            if $p = p^{\prime}$ then $\equivc \circ q$ = $\equivc^{\prime} \circ q^{\prime}$
        \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&]
        \& \dfiberc^a \times \dfiberc^b 
        \arrow[ld, "p"', color=fiber] 
        \arrow[rd, "q \circ \equivc"] \&     \\
        \dfiberc^a \& \& M^a \\
        \& \dfiberc^a \times \dfiberc^c 
        \arrow[lu, "p^{\prime}", color=fiber] 
        \arrow[ru, " q^{\prime} \circ\equivc^{\prime}"'] \&    
      \end{tikzcd}
    \end{equation*}}         
        \item[both]{given $\dsectionc^{a} \in \sheafc_{\dbasec_a, \dtotalc_a}, \dsectionc^{b} \in \sheafc_{\dbasec_b, \dtotalc_b}$ and $\dbasepointc \in \dbasec_{a}\bigsqcup\limits_{\dbasec_{c}} \dbasec_{b}$ then $q(\equivc(\dsection^a(\dbasepointc))) = q^{\prime}(\equivc(\dsectionc^b(\dbasepointc)))$ when $p(\dfiberc^{a}\restriction_{\dbasepointc}) = p^{\prime}(\dfiberc^{b}\restriction_{\dbasepointc})$}
    \end{description}
\end{frame}

\begin{frame}{"Valid" viz?}
    \begin{equation*}
        \label{eq:artist:artist_sheaf}
        \begin{tikzcd}[ampersand replacement = \&, column sep=tiny, row sep=huge]
            \onslide*<1-|handout:1>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}} 
            \&  \& 
            \onslide*<2-|handout:1>{\textcolor{set}{\big\{}\gsectionc 
              \bigm{\vert} \delta(\vartistc(\dfuncc_{\dtotalc}(\dsectionc))) = \dfuncc_{M}(\delta(\gsectionc)) \textcolor{set}{\big\}}} 
            \onslide*<2-|handout:1>{\arrow[ll, "\textcolor{set}{\mathlarger{\mathlarger{\supset}}}" description, hook', color=white]} \\ 
            \&  \& \\
            \onslide*<1-|handout:1>{\opensetgc} 
            \onslide*<1-|handout:1>{\arrow[uu, "\sheafc_{\gbasec,\gtotalc}", color=sheaf, maps to]} 
            \onslide*<2-|handout:1>{\arrow[rruu, "\vartistc(\sheafc_{\dtotalc})\coloneqq \sheafc_{\vartistc}" description, dashed, color=sheaf, maps to]} 
            \&  \& 
        \end{tikzcd}
    \end{equation*}
\end{frame}

@@

\begin{frame}{Components to Graphic}
    \begin{figure}
        \includegraphics[scale=.15]{../paper/figures/qhat.png}
    \end{figure}
\end{frame}

\begin{comment}
\begin{frame}{Scatter: $\vmark(xpos, ypos)(\alpha, \beta)$}
    \begin{figure}[H]
        \begin{overprint}
            \onslide<1|handout:0>\includegraphics[width=1\linewidth]{figures/math/scatter_q.png}
            \onslide<2|handout:0>\includegraphics[width=1\linewidth]{figures/math/scatter_with_s.png}
        \end{overprint}
    \end{figure}   
\end{frame}

\begin{frame}{Line: $\vmark(xpos, \hat{n_{1}}, ypos, \hat{n_{2}})(\alpha, \beta)$ }
    \begin{figure}[H]
        \begin{overprint}
            \onslide<1|handout:0>\includegraphics[width=1\linewidth]{figures/math/line_q.png}
            \onslide<2|handout:0>\includegraphics[width=1\linewidth]{figures/math/line_with_s.png}
        \end{overprint}
    \end{figure}   
\end{frame}

\begin{frame}{Image $\vmark(xpos, ypos, color)$}
    \begin{figure}[H]
        \includegraphics[width=1\textwidth]{figures/math/image.png}
    \end{figure}
\end{frame}

\begin{frame}{Build \vmark\ over \dbase: \vmarkd}
\begin{figure}[H]
    \includegraphics[width=1\textwidth]{figures/math/q_hat.png}
\end{figure}
\begin{equation*}\label{eq:qhat_q_s}
    \vmarkd(\vsection(\dbasepoint))(\gbasepoint) \coloneqq \vmark((\vsectionpull)(\gbasepoint))
\end{equation*} 
\end{frame}

\begin{frame}{Composition of artists $+ \coloneqq \sqcup \dtotal_{i}$} 
    \begin{figure}
        \includegraphics[width=1\textwidth]{figures/math/exploding_artist.png}
    \end{figure}
\end{frame}

\section{Code}
\begin{frame}{TEAM driven rearchitecture of Matplotlib}
    \begin{itemize}
        \item complex visualizations
        \pause 
        \item structure preserving maps from data to visual
        \begin{itemize}
            \item data and graphics have equivalent continuity
            \item properties are equivariant under monoid actions
        \end{itemize}  
        \pause
        \item fiber bundles are an abstraction
        \begin{itemize}
            \item topologically complex heterogenous data 
            \item target display spaces
        \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}[fragile]{How do we make things?}
    \begin{figure}[H]
        \begin{subfigure}{0.49\textwidth}
            \includegraphics[width=\textwidth]{figures/code/scatter_0.png}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \includegraphics[width=\textwidth]{figures/code/line_1.png}
        \end{subfigure}
    \end{figure}
    \begin{columns}
    \column{0.49\textwidth}
    \begin{minted}{python}
    fig, ax = plt.subplots()
    artist = Point(data, transforms)
    ax.add_artist(artist)
    \end{minted}
    \column{.49\textwidth}
    \begin{minted}{python}
    fig, ax = plt.subplots()
    artist = Line(data, transforms)
    ax.add_artist(artist)
    \end{minted}
    \end{columns}
\end{frame}

\subsection{Artist}
\begin{frame}[fragile]{ \vchannel}
    \begin{minted}{python}
    cmap =  color.Categorical({'true':'deeppink', 'false':'deepskyblue'})
    transforms = {'x': {'name': 'v4', 'encoder': lambda x: x},
                    'y': {'name': 'v2', 'encoder': lambda x: x},
                    'facecolors': {'name':'v3', 'encoder': cmap}, 
                    's':{'name': None , 
                        'encoder': lambda _: itertools.repeat(.02)}}
    \end{minted}
    \begin{itemize}
        \item \mintinline{python}{lambda x: x} is identity \vchannel\
        \item \mintinline{python}|{'name':None}| map into \vfiber\ without corresponding \dsection\
        \item \mintinline{python}{color.Categorical} is custom \vchannel
    \end{itemize}
\end{frame}

\begin{frame}[fragile]{\vartist} %% rewrite w/ letters in talk
    \begin{minted}{python}
        class ArtistClass(matplotlib.artist.Artist):
            def __init__(self, E, V, *args, **kwargs):
                # set properties that are specific to the artist
                # stash the input E and V
                super().__init__(*args, **kwargs)

            def qhat(self, **args):
                # set the properties of the graphic

            def draw(self, renderer):
                # returns tau, indexed on fiber then key 
                tau = self.E.view(self.axes) 
                # visual channel encoding applied fiberwise 
                visual = {p_i: nu_i(tau_i)
                          for p_i, nu_i, tau)i 
                          in zip(self.V, tau)}
                self.qhat(**visual)
                # pass configurations off to the renderer
                super().draw(renderer)
        \end{minted}
\end{frame}

\begin{frame}[fragile]{\vmarkd}
\begin{minted}{python}
    class Point(mcollections.Collection):
        def assemble(self, x, y, s, facecolors='C0' ):
            # construct geometries of the circle glyphs in visual coordinates
            # set attributes of glyphs

    class Line(mcollections.LineCollection):
        def assemble(self, x, y, color='C0'):
            # assemble line marks as set of segments 
    \end{minted}
\end{frame}

\subsection{Data}
\begin{frame}[fragile]{Continuity}
    \begin{minted}{python}
class PointData: 
    # Fiberbundle is consistent across all sections
    FB = FiberBundle({'tables': ['vertex']},  
        {'v1': float, 'v2': str, 'v3': float})
    def tau(self, k):
        return # tau evaluated at one point k

class LineData: 
    FB = FiberBundle({'tables': ['edge']},
                {'x' : float, 'y':  float, 'color':mtypes.Color()})
    def tau(self, k): 
        return # tau evaluated on interval k
    \end{minted}
\end{frame}

\begin{frame}[fragile]{Same Artist, Different \dtotal}
    \begin{figure}[H]
        \begin{subfigure}{0.49\textwidth}
            \includegraphics[width=\textwidth]{figures/code/linec_1.png}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \includegraphics[width=\textwidth]{figures/code/lined_1.png}
        \end{subfigure}
    \end{figure}
\begin{minted}{python}
LineData(FB, edge_table, vertex_table, connect=True)
LineData(FB, edge_table, vertex_table, num_samples=2, connect=False)
\end{minted}
\end{frame}

\begin{frame}{Proposed Work}
\begin{figure}
    \includegraphics[width=1\textwidth]{figures/intro/gantt.png}
\end{figure}
\end{frame}

\begin{frame}{Acknowledgments}
    \begin{itemize}
        \item Professor Michael Grossberg and Dr. Thomas Caswell
        \item Professor Haralick, Professor Vo, Professor Manovich, Dr. Hanwell
        \item Matplotlib development team 
        \item CZI EOSS (grant number 2019-207333) from the Chan Zuckerberg Initiative DAF, an advised fund of Silicon Valley Community Foundation
    \end{itemize}

\begin{frame}[allowframebreaks]{References}
\printbibliography
\end{frame}
\appendix

\begin{frame}{Bertin Retinal Variables}
    \begin{figure}
        \includegraphics[width=.7\textwidth]{figures/intro/retinal_variables.png}
        \caption{This tabular form of Bertin's retinal variables is from Understanding Graphics \cite{malamedInformationDisplayTips2010} who reproduced it from Krygier and Wood's \textit{Making Maps: A Visual Guide to Map Design for GIS}\cite{krygierMakingMapsVisual2005}}
    \end{figure}
\end{frame}

\begin{frame}{Fiber is all possible values a variable can be \cite{spivakDatabasesAreCategories2010,spivakSIMPLICIALDATABASES}}
    Given a space of all possible values \ftotal\
    \begin{equation*}
        \label{eq:data_types}
        \begin{tikzcd}[ampersand replacement=\&]
            \fttype \arrow[r] \arrow[d, "\pi_{\fsection}"'] \& \ftotal \arrow[d, "\pi"] \\
            \fnames \arrow[r, "\fsection"']                  \& \ftypes       
        \end{tikzcd}
    \end{equation*}
    a fiber component is the restricted space $\ftotal_{\fsection(\fname)}$. 
    \begin{equation*}
        \dfiber = \ftotal_{\fsection(\fname)} = \ftotal_{\ftype} 
    \end{equation*}
    \begin{description}
        \item[\ftypes] data types of the variables in the dataset 
        \item[\ftotal] disjoint union of all values of type $\ftype \in \ftypes$ 
        \item[\fnames] variable names, $\fname \in \fnames$
        \item[\fttype] \ftotal\ restricted to the data type of a named variable   
    \end{description}
\end{frame}

\begin{frame}{Monoid actions}
    A monoid \monoid\ is a set with
    \begin{description}
        \item[associative binary operator] $\ast:\monoid \times \monoid\rightarrow \monoid$
        \item[identity element] $e\in \monoid$ such that $e\ast a= a \ast e = a$ for all $a \in \monoid$. 
    \end{description}
    \begin{block}{left monoid action}
    A set \dfiber\ with an action\cite{nlab:action} $\bullet: \monoid\times \dfiber \rightarrow \dfiber$ with the properties:
        \begin{align*}
            \textbf{associativity}\;& \text{for all } f,g \in \monoid \text{ and } x\in \dfiber,\, f\bullet(g\bullet x) = (f\ast g) \bullet x\\
            \textbf{identity}\;& \text{for all } x\in \dfiber, e\in \monoid,\,  e\bullet x = x 
        \end{align*}
    \end{block}
\end{frame}

\begin{frame}{Keeping track of sections with sheafs}
    Restriction maps of a sheaf describe how local $\iota^*\dsection$ can be glued into larger sections \cite{ghristElementaryAppliedTopology2014,ghristHomologicalAlgebraData2018}
    \begin{equation*}
        \label{eq:sheaf}
        \begin{tikzcd}[ampersand replacement=\&]
            \iota^*\dtotal \arrow[d, "\pi"'] \arrow[r, "\iota^*", hook]             \& \dtotal \arrow[d, "\pi"']                  \\
            U \arrow[r, "\iota", hook] \arrow[u, "\iota^{*}\dsection"', bend right] \& \dbase \arrow[u, "\dsection"', bend right]
        \end{tikzcd}
    \end{equation*}
    The inclusion map $\iota: U \rightarrow \dbase$ pulls \dtotal\ over $U$ such that the pulled back $\iota^*\dsection$ only contains records over $U \subset \dbase$.
\end{frame}

\begin{frame}{Rendering: Define a Pixel}
    \begin{columns}
        \column{0.5\textwidth}
        Given a pixel
        \begin{equation*}
        p=\left[y_{top}, y_{bottom}, x_{right}, x_{left}\right]
        \end{equation*}
        the inverse map of the bounding box 
        \begin{equation*}
        \gbase_{p} ={\gsection_{xy}}^{-1}(p)
        \end{equation*}
        is a region $\gbase_p \subset \gbase$ such that 
        \begin{align}
            \scriptstyle r_p &= \scriptstyle \iint\limits_{S_p} \rho_r(s)ds^{2}\\
            \scriptstyle g_p &= \scriptstyle \iint\limits_{S_p} \rho_g(s)ds^{2}\\
            \scriptstyle  b_p &= \scriptstyle \iint\limits_{S_p} \rho_b(s)ds^{2}
        \end{align}
        yields the color of the pixel. 
        \column{0.5\textwidth}
        \begin{figure}[H]
            \includegraphics[width=\textwidth]{figures/math/render.png}
        \end{figure}
    \end{columns}
\end{frame}

\begin{frame}{$\mathcal{A}:\mathcal{E}\rightarrow\mathcal{E}$}
    The topological artist is a sheaf map
    \begin{equation*}
    \vartist: \mathcal{O}(\dtotal) \rightarrow \mathcal{O}(\gtotal)
    \end{equation*}
    that carries homomorphism of monoid actions $\varphi: \monoid \rightarrow \monoid^{\prime}$ 
    \cite{cegarraCohomologyMonoidsOperators2019} 
    \begin{equation*}
    \vartist(m\cdot \delement) = \varphi(m)\cdot \vartist(\delement) 
    \end{equation*}
\end{frame}

\begin{frame}{Visual Channel Encoders}
    We define the visual transformers \vchannel\ on components of the data bundle $\dsection_{i}$
    \begin{equation*}
        \label{eq:nu_expanded}
        \{\vchannel_{0}, \ldots, \vchannel_{n}\}: \{\dsection_{0}, \ldots, \dsection_{n}\} \mapsto \{\vsection_{0}, \ldots, \vsection_{n}\}
    \end{equation*}
    as the set of equivariant maps with the constraint 
    \begin{equation*}
        \vchannel_i(m_{\delement}(\dtotal_i)) = \varphi(m_{\delement})(\vchannel_i(\dtotal_i))
    \end{equation*} 
    where $\varphi:\monoid\rightarrow \monoid^{\prime}$ carries a homomorphism of monoid actions. 
\end{frame}

\begin{frame}{\vfiber\ Components}    
\begin{table}[H]
    \renewcommand{\arraystretch}{2}
    \begin{tabulary}{\textwidth}{|l|L|l|}\hline
     $\bm{\vchannel_{i}}$                      & $\bm{\vsection_{i}}$                                                            & $\bm{codomain(\vchannel_{i}) \subset \vfiber_{i}}$  \\ \hline                                              
    position                    & x, y, z, theta, r                                                          & $\mathbb{R}$   \\ \hline
    size                        & linewidth, markersize                                            & $\mathbb{R}^{+}$   \\ \hline
    shape                       & markerstyle                                                      & $\{f_{0}, \ldots, f_{n}\}$ \\ \hline
    color                       & color, facecolor, markerfacecolor, edgecolor  & $\mathbb{R}^{4}$ \\ \hline
    \multirow{2}{*}{texture}    & hatch                                                            & $\mathbb{N}^{10}$\\\cline{2-3}
                                & linestyle                                                        & $(\mathbb{R}, \mathbb{R^+}^{n, n\%2=0})$ \\ \hline              
    \end{tabulary}
    \label{tab:mpl_visual_variable_fiber}
\end{table}
\end{frame}
\begin{frame}{Monoid Equivariance: Partial Orders}
    \begin{figure} %break out steps/reveal
        \includegraphics[width=1\textwidth]{figures/math/monoid_equivariant.png}
    \end{figure}
\end{frame}

\begin{frame}{Glyph}
    The glyph is the graphic generated by $\vmark(\gbase_{\dbasepathpoint})$ where the path connected components $\dbasepath \subset \dbase$ are defined 
    \begin{equation*}
    \dbasepath = \{\dbasepathpoint \in \dbase \text{ s. t. } \exists \gamma \text{ s.t. } \gamma(0)=\dbasepoint \text{ and }\gamma(1)=\dbasepathpoint\}
    \end{equation*}
    such that the  path $\gamma$ from \dbasepoint\ to \dbasepathpoint\ is a continuous function from the interval [0,1] and $\gbase_{\dbasepathpoint}$ is the region
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
            \gtotal \arrow[r, shift left] \& \gbase_\dbasepathpoint \arrow[rr, "\vindex(\gbasepoint)", shift left] \arrow[l, "\gsection(\gbase_\dbasepathpoint)"] \& \& \dbasepath_{\dbasepoint} \arrow[ll, "\vindex^{-1}(\dbasepath)"]
            \end{tikzcd}
        \label{eq:mark}
    \end{equation*}
    such that the glyph is differentiable, in keeping with Ziemkiewicz and Kosara's description of a glyph\cite{ziemkiewiczEmbeddingInformationVisualization2009}.
\end{frame}

\begin{frame}{Artist Equivalance class}
    When artists share a base space 
    \begin{equation*}
        \dbase_2 \hookrightarrow \dbase_1
    \end{equation*}
    a composition operator can be defined such that the the artists can be considered to be acting on different components of the same section. 
\end{frame}

>>>>

\subsubsection{Natural Transforms}
\begin{frame}{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}
    \onslide<|handout:1>{
    \adjustbox{scale=3, center}{
        \begin{tikzcd}[ampersand replacement=\&]
            \& {} \arrow[dd, "\alpha" , Rightarrow, shorten=1.5em, color=nattran] \&             \\
          \textcolor{source}{\mathcal{C}} \arrow[rr, "F", bend left, color=functor, maps to] \arrow[rr, "G"', bend right, color=functor, maps to] \& \& \textcolor{target}{\mathcal{D}} \\
            \& {} \&            
          \end{tikzcd}}}
\end{frame}

@@

\subsubsection{Pullback and Pushforward}
\begin{frame}{}

@@

    \only<0|handout:1>{% data sheaf

@@

    \only<0|handout:4>{%pulled back data sheaf

@@

    \only<0|handout:2>{% graphic sheaf

@@

    \only<0|handout:5>{%pushed forward sheaf

@@

            \item $\cgamma{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc}} \ni \vindexpushc\gsectionc: \opensetc \rightarrow \vindexpushc \gfiberc\restriction_{\opensetc}$
            \item $\vindexpushc\gsectionc(\dbasepointc) = \gsectionc\restriction_{\vindexpre(\dbasepointc)} = \gsectionc(\gbasepointc)\;\forall \gbasepointc \in \vindexpre(\dbasepointc)$ 

@@

\begin{frame}{Example: Scatter Plot}
    \begin{figure}
        \includegraphics[scale=.1]{figures/math/push_pull_scatter.png}
    \end{figure}
\end{frame}

\begin{frame}{Example: Line Plot}
    \begin{figure}
        \includegraphics[scale=.1]{figures/math/push_pull_line.png}
    \end{figure}
\end{frame}

\begin{frame}{Example: Image}
    \begin{figure}
        \includegraphics[scale=.1]{figures/math/push_pull_image.png}
    \end{figure}
\end{frame}

\begin{frame}{Example: Heatmap}
    \begin{figure}
        \includegraphics[scale=.1]{figures/math/push_pull_heat.png}
    \end{figure}
\end{frame}

\begin{frame}{Example: Sphere}
    \begin{figure}
        \includegraphics[scale=.1]{figures/math/push_pull_sphere.png}
    \end{figure}
\end{frame}

@@

\begin{frame}
    \frametitle<0|handout:1>{Artist: $\vartistc: \sheafc_{\dbasec, \dtotalc} \rightarrow \sheafc_{\gbasec, \gtotalc}$}
    \frametitle<0|handout:2>{Data Space: $\vartistc_{\opensetc}: \sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\Rightarrow} \vindexpushc\sheafc_{\gbasec, \gtotalc}$}
    \frametitle<0|handout:3>{Display Space: $\vartist_{\opensetgc}: \vindexpullc\sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\Rightarrow} \sheafc_{\gbasec, \gtotalc}$}
    \frametitle<0|handout:4>{Artist: $\vartistc: \cgamma{\opensetc}{\dtotalc} \rightarrow \cgamma{\opensetgc}{\gtotalc}$}
    \onslide*<0|handout:1,4>{
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<0|handout:1>{\sheafc_{\gbasec, \gtotalc}} 
          \onslide*<0|handout:4>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}}
          \onslide*<0|handout:1,4>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \& \& 
          \onslide*<0|handout:1>{\vindexpushc\sheafc_{\gbasec, \gtotalc}}
          \onslide*<0|handout:4>{\cgamma{\opensetc}{\vindexpushc \gtotalc\restriction_{\opensetc}}}
          \\
          \& \& \\
          \onslide*<0|handout:1>{\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}}
          \onslide*<0|handout:4>{\cgamma{\opensetgc}{\vindexpullc \dtotalc\restriction_{\opensetgc}}}
          \onslide*<0|handout:1,4>{\arrow[uu, "\vartistc_{\opensetgc}", color=artist, Rightarrow]}
          \&  \& 
          \onslide*<0|handout:1>{\sheafc_{\dbasec, \dtotalc}}
          \onslide*<0|handout:4>{\cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}}
          \onslide*<0|handout:1,4>{\arrow[ll, "\textcolor{functor}{\vindexpull}", color=functor]} 
          \onslide*<0|handout:1,4>{\arrow[uu, "\vartistc_{\opensetc}"', color=artist, Rightarrow]}
          \onslide*<4-|handout:1,4>{\arrow[lluu, "\vartistc"' description, dashed, color=artist, Rightarrow]}
        \end{tikzcd}
    \end{equation*}}

@@

\subsection{Equivariance}
\begin{frame}{Transform Data}
    \begin{block}{Fiber Bundle Category}
        \begin{description}[style=newline]
            \item[object] $\dfiberc \hookrightarrow \dtotalc \xrightarrow{\pi} \dbasec$
            \item[morphisms] $\dfuncc: \dtotalc \rightarrow \dtotalc$ 
        \end{description}
    \end{block}
    \begin{block}{Fiber Category}
        The fiber $\dfiberc$ is the sole object of an arbitrary category $\mathcal{C}$.
        The morphisms on the fiber are $Hom(\dfiberc, \dfiberc)$
    \end{block}

@@

    \begin{alertblock}{Artist Constraints}
        \begin{align*}
            \vartistc(\dsectionc^{a}) = \vartistc(\dsectionc^{b}) &\centernot\implies \dsectionc^a = \dsectionc^b \\
            \vartistc(\dsectionc^{a})  = \vartistc(\dsectionc^{b}) &\implies \vartistc(\dfuncc_{\dtotalc}(\dsectionc^{a})) = \vartistc(\dfuncc_{\dtotalc}(\dsectionc^{b}))
        \end{align*}
    \end{alertblock}
\end{frame}

\begin{frame}{Equivariant $\dfunchc$}
    \note{Maybe move to implementation section}
        \begin{equation*}
            \begin{tikzcd}[ampersand replacement=\&]
            \opensetgc 
            \arrow[rr, "\vindexc", color=functor] 
            \arrow[dd, "\dfunchc_{\gbasec}"', dashed, color=action] 
            \&  \& 
            \opensetc 
            \arrow[dd, "\dfunchc_{\dbasec}", color=action] \\
            \&  \& \\
            \opensetgc^{\prime} 
            \arrow[rr, "\vindexc"', color=functor]
            \&  \& 
            \opensetc^{\prime}\\
            \underbrace{\dbasec \times {[0,1]}^{m}}_{\gbasec} \arrow[rr,"\vindex", maps to, color=functor] \& \& \dbasec
            \end{tikzcd}
        \end{equation*}
\end{frame}

@@

\begin{frame}{Complex data}
    \begin{description}[style=newline]
        \item[combining continuities]{given $\dbasepointc_{a} \in \dbasec_{c} \subset \dbasec_{a}$ and $\dbasepointc_{b} \in \dbasec_{c} \subset \dbasec_{b}$, if $\dbasepointc_{a} = \dbasepointc_{b}$ then $\equivc(\dsectionc(\dbasepointc_{a})) = \equivc(\dsectionc(\dbasepointc_{b}))$ for all $\dbasepointc_{a}, \dbasepointc_{b} \in \dbasec_{a}\bigsqcup\limits_{\dbasec_{c}} \dbasec_{b}$}
        \item[shared fibers]{
            if $p = p^{\prime}$ then $\equivc \circ q$ = $\equivc^{\prime} \circ q^{\prime}$
        \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&]
        \& \dfiberc^a \times \dfiberc^b 
        \arrow[ld, "p"', color=fiber] 
        \arrow[rd, "q \circ \equivc"] \&     \\
        \dfiberc^a \& \& M^a \\
        \& \dfiberc^a \times \dfiberc^c 
        \arrow[lu, "p^{\prime}", color=fiber] 
        \arrow[ru, " q^{\prime} \circ\equivc^{\prime}"'] \&    
      \end{tikzcd}
    \end{equation*}}         
        \item[both]{given $\dsectionc^{d} \in \sheafc_{\dbasec_{d}, \dtotalc_{d}}, \dsectionc^{e} \in \sheafc_{\dbasec_{e}, \dtotalc_{e}}$ and $\dbasepointc \in \dbasec_{d}\bigsqcup\limits_{\dbasec_{f}} \dbasec_{e}$ then $q(\equivc(\dsection^{d}(\dbasepointc))) = q^{\prime}(\equivc(\dsectionc^{e}(\dbasepointc)))$ when $p(\dfiberc^{d}\restriction_{\dbasepointc}) = p^{\prime}(\dfiberc^{e} \restriction_{\dbasepointc})$}
    \end{description}
\end{frame}

\begin{frame}{"Valid" viz?}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, column sep=tiny, row sep=huge]
            \onslide*<1-|handout:1>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}} 
            \&  \& 
            \onslide*<2-|handout:1>{\textcolor{set}{\big\{}\gsectionc \bigm{\vert} 
              \delta(\vartistc(\dfuncc_{\dtotalc}(\dsectionc))) = \dfuncc_{M}(\delta(\gsectionc)) \textcolor{set}{\big\}}} 
            \onslide*<2-|handout:1>{\arrow[ll, "\textcolor{set}{\mathlarger{\mathlarger{\supset}}}" description, hook', color=white]} \\ 
            \&  \& \\
            \onslide*<1-|handout:1>{\opensetgc} 
            \onslide*<1-|handout:1>{\arrow[uu, "\sheafc_{\gbasec,\gtotalc}", color=sheaf, maps to]} 
            \onslide*<2-|handout:1>{\arrow[rruu, "\vartistc(\sheafc_{\dtotalc})\coloneqq \sheafc_{\vartistc}" description, dashed, color=sheaf, maps to]} 
            \&  \& 
        \end{tikzcd}
    \end{equation*}
\end{frame}

\begin{comment}

@@

\begin{frame}{Components to Graphic}
    \begin{figure}
        \includegraphics[scale=.15]{../paper/figures/qhat.png}
    \end{figure}
\end{frame}
\end{comment}
\end{document}
